Details matter: Similar-looking host galaxies can produce different merging compact binary populations

### 2015-04-22 paper/paper.tex
paper.tex: updating caption and action items

\begin{figure}
\includegraphics[width=\columnwidth]{Figures/zvst}
\caption{\label{fig:TwoGalaxies}\textbf{Star formation and metallicity versus time}:  \emph{Left panel}: Star formation history $\dot{M}_{*}$
  versus time.  Red corresponds to galaxy A (``boring'') and blue to gaalxy B (``exciting'').  
\emph{Right panel}: A plot of the  metallicity $Z$ of recently-formed stars versus time.  Solid red and black lines show
the mean metallicity; dotted lines correspond to  90\% of newly-born stars have lower metallicity,   or 10\% of
newly-born stars have greater metallicity.
}
\end{figure}

@@

\subsection{Tidal disruption and black hole mass versus metallicity}
At merger, black holes may promptly engulf a companion neutron star \editremark{same papers as for Brandon:Foucart,
  etc}.  Without  a tidal disruption event prior to merger, the prospects for associated electromagnetic counterparts
are severely diminished.  
To quantify this effect

DISCUSSION: could we explain the redshift distribution of short GRBs this way?

@@

** May want more Z bins to make sure we resolve it. Our differences between predictions are not huge

*** or rewrite script to use numpy on raw star data.  Use 'starmetal.dat': last colum is age.

** Clear that low-Z matters a lot

>>>>

\begin{figure*}
\includegraphics[width=\columnwidth]{Figures/sfh}
\includegraphics[width=\columnwidth]{Figures/zvst}
\caption{\label{fig:TwoGalaxies}\textbf{Star formation and metallicity versus time}:  \emph{Left panel}: Star formation history $\dot{M}_{*}$
  versus time.  Black corresponds to galaxy A (``boring'') and red to gaalxy B (``exciting'').  
\emph{Right panel}: A plot of the  metallicity $Z$ of recently-formed stars versus time.  Solid red and black lines show
the mean metallicity; dotted lines correspond to  90\% of newly-born stars have lower metallicity,   or 10\% of
newly-born stars have greater metallicity.  When these two galaxies are $2-3\unit{Gyr}$ old, prior to the first major
merger of  near the peak of their
star-forming history, newly-born stars are created with significantlydifferent metallicity.  Additionally, prior to the
second major merger of galaxy B at $\simeq 6\unit{Gyr}$, stars form in the ``exciting'' galaxy at a systematically lower
metallicity than in the ``boring'' counterpart.
}
\end{figure*}

@@

\subsection{Tidal disruption and black hole mass versus metallicity}
At merger, black holes may promptly engulf a companion neutron star \editremark{same papers as for Brandon:Foucart,
  etc}, unless they have sufficiently small mass and sufficiently large spin.  Without  a tidal disruption event prior to merger, the prospects for associated electromagnetic counterparts
are severely diminished.  
%
The black hole mass and possibly spin in black hole-neutron star binaries can depend sensitively on binary formation
channels.  Because of the extremely narrow range of masses that permit tidal disruption in BH-NS binaries, small changes
in the mass distribution can produce significant changes in the electromagnetically detected population.
%
To quantify this effect, we adopt a simple formula for tidal disruption of neutron stars in BH-NS binaries and a simple
phenomenological model for the metallicity-dependent mass distribution of BHs in BH-NS binaries

\editremark{calibrate mass distribution to synthetic universe/Dominik - but also allow reversed trend}
DISCUSSION: could we explain the redshift distribution of short GRBs this way?

@@

** Modify script to include tidal disruption options for BHs

** plot 'stanard' results for NS-NS

** set scale to be physical units -- some ad-hoc factors used
